% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Ongoing}   {Research Intern | App Development}{Chandhar Research Labs}{Chennai}
    {April 2021} {
                      \begin{itemize}
                        \item Development of Shadow Lab application for demonstrating the shadowing effect in 4G LTE UE.                       
                        \item Integration with Collaborative Radio Frequency Observatory (CRFO)
                        \item Addition of new features like band information, heatmaps and integration with Firebase.
                        \item Using collected data for classification of type of environment (indoor/outdoor) using various models
                      \end{itemize}
                    }
                    {Java, Android Studio, Firebase, 4G LTE, Python}
  \emptySeparator
  \experience
    {Jan 2021}   {Intern | Computer Vision}{Findmind Analytics Pvt. Ltd.}{Vellore}
    {Nov 2020} {
                      \begin{itemize}
                        \item Training, testing and deployment of DarkNet-YOLO based model for masking sensitive data in Aadhar.                       
                        \item Finetuning custom OCR model based on Tesseract LSTM for extraction of user data in PAN cards.
                        \item Implementation of parallel detection/masking/OCR using multiprocessing library for both Aadhar and PAN models.                        
                        \item Generation of real-like synthetic data for improving PAN OCR accuracy. 
                      \end{itemize}
                    }
                    {DarkNet, YOLO, Tesseract, Tensorflow, Keras, Python}
%   \emptySeparator
%   \experience
%   {Novembre 2007}  {Ingénieur d'étude}{IBM}{France}
%   {Février 2007}   {
%                       Implémentation d'une solution de paiement NFC sur téléphones portables (\href{http://www.nouvo.ch/s-007}{vidéo}) 
%                       dans le cadre du projet Campus Nova pour le Crédit Agricole  
%                       \begin{itemize}
%                         \item Implémentation d'un porte monnaie électronique                                            
%                         \item Intégration avec une plateforme de paiement en ligne  
%                       \end{itemize}
%                   }
%                   {J2ME, Java Card, DB2, \emph{WAS}}  
\end{experiences}
